### 2020-02-22 Common/chapters/paper_reproduction.tex
Julien and Johan: script options update

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|llll|}
\hline
\rowcolor[HTML]{DAE8FC} 
\textbf{Command}            & \textbf{Description}                                                                                                                                                                                                & \textbf{Required}                                                           & \textbf{Type} \\ \hline
\textbf{--trainingSet1}     & Training set  path                                                                                                                                                                                                  & True                                                                        & String        \\ \hline
\textbf{--validationSet1}   & Validation set path                                                                                                                                                                                                 & True                                                                        & String        \\ \hline
\textbf{--batchsize}        & Number of samples per batch                                                                                                                                                                                         & True                                                                        & Int           \\ \hline
\textbf{--nbepochs}         & Number of epochs the training phase has to last                                                                                                                                                                     & True                                                                        & Int           \\ \hline
\textbf{--lr}               & Learning rate used in the optimizer                                                                                                                                                                                 & \begin{tabular}[c]{@{}l@{}}False\\ Default: 1e-3\end{tabular}               & Float         \\ \hline
\textbf{--lossfunction}     & \begin{tabular}[c]{@{}l@{}}Loss function name\\{[}CrossEntropyLoss, L1Loss, MSELoss{]}\end{tabular}                                                                                                            & \begin{tabular}[c]{@{}l@{}}False\\ Default: 'CrossEntropyLoss'\end{tabular} & String        \\ \hline
\textbf{--cuda-device}      & GPU name to run the experiment                                                                                                                                                                                      & \begin{tabular}[c]{@{}l@{}}False\\ Default: 'cuda'\end{tabular}             & String        \\ \hline
\textbf{--modeltoload}      & \begin{tabular}[c]{@{}l@{}}Pretrained model name \\If given, load it, otherwise randomly initialize it\end{tabular}                                                                                     & \begin{tabular}[c]{@{}l@{}}False\\ Default: ""\end{tabular}                 & String        \\ \hline
\textbf{--dropout}          & Dropout probability                                                                                                                                                                                                 & \begin{tabular}[c]{@{}l@{}}False\\ Default: 0.3\end{tabular}                & Float         \\ \hline
\textbf{--optimized-metric} & \begin{tabular}[c]{@{}l@{}}Metric to optimize\\ The best model during the training will be saved according to it\\{[}'auc', 'accuracy', 'precision', 'recall', 'f1score', 'specificity'{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}False\\ Default: 'auc'\end{tabular}              & String        \\ \hline
\textbf{--outputdirectory}  & Root of the output directory used by Tensorboard to save the models                                                                                                                                                 & True                                                                        & String        \\ \hline
\end{tabular}%
}
\caption{Complete list of script options}
\label{fig:paper_reproduction_options}
\end{table}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
\resizebox{\textwidth}{!}{%
\begin{tabular}{|llll|}
\hline
\rowcolor[HTML]{DAE8FC} 
\textbf{Command}            & \textbf{Description}                                                                                                                                                                                                & \textbf{Required}                                                           & \textbf{Type} \\ \hline
\textbf{--trainingset}     & Training set  path                                                                                                                                                                                                  & True                                                                        & String        \\ \hline
\textbf{--validationset}   & Validation set path                                                                                                                                                                                                 & True                                                                        & String        \\ \hline
\textbf{--batchsize}        & Number of samples per batch                                                                                                                                                                                         & True                                                                        & Int           \\ \hline
\textbf{--nbepochs}         & Number of epochs the training phase has to last                                                                                                                                                                     & True                                                                        & Int           \\ \hline
\textbf{--lr}               & Learning rate used by the optimizer                                                                                                                                                                                 & \begin{tabular}[c]{@{}l@{}}False\\ Default: 1e-3\end{tabular}               & Float         \\ \hline
\textbf{--lossfunction}     & \begin{tabular}[c]{@{}l@{}}Loss function name\\{[}CrossEntropyLoss, L1Loss, MSELoss{]}\end{tabular}                                                                                                            & \begin{tabular}[c]{@{}l@{}}False\\ Default: 'CrossEntropyLoss'\end{tabular} & String        \\ \hline
\textbf{--cudadevice}      & GPU name to run the experiment                                                                                                                                                                                      & \begin{tabular}[c]{@{}l@{}}False\\ Default: 'cuda'\end{tabular}             & String        \\ \hline
\textbf{--modeltoload}      & \begin{tabular}[c]{@{}l@{}}Pretrained model name \\If given, load it, otherwise randomly initialize it\end{tabular}                                                                                     & \begin{tabular}[c]{@{}l@{}}False\\ Default: ''\end{tabular}                 & String        \\ \hline
\textbf{--dropout}          & Dropout probability                                                                                                                                                                                                 & \begin{tabular}[c]{@{}l@{}}False\\ Default: 0.3\end{tabular}                & Float         \\ \hline

\textbf{--inputchannel}     & \begin{tabular}[c]{@{}l@{}}Number of channels of the input images\\{[}1,3{]}\end{tabular}                                                                                                            & \begin{tabular}[c]{@{}l@{}}True\end{tabular} & Int        \\ \hline

\textbf{--optimizedmetric} & \begin{tabular}[c]{@{}l@{}}Metric to optimize\\ The best model during the training will be saved according to it\\{[}'auc', 'accuracy', 'precision', 'recall', 'f1score', 'specificity'{]}\end{tabular} & \begin{tabular}[c]{@{}l@{}}False\\ Default: 'auc'\end{tabular}              & String        \\ \hline
\textbf{--outputdirectory}  & Root of the output directory used by Tensorboard to save the models                                                                                                                                                 & True                                                                        & String        \\ \hline
\end{tabular}%
}
\caption{Complete list of script options}
\label{fig:paper_reproduction_options}
\end{table}
